3.9: Logarithmic Regression - Class Notes

### 2019-12-06 content/assignment/02-exam.Rmd
Add HW 5 answers, HW 6 and answers, finalize schedule page (put extra content after final), add final exam prep

---
title: "Midterm Exam"
editor_options: 
  chunk_output_type: console
---

@@

*Thursday, October 17*

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/midtermconcepts.pdf)
- [<i class="fas fa-external-link-square-alt"></i> Review Questions Slides](/slides/midterm-review.html)

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/01-old-exam.pdf)

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/midtermformulas.pdf)

>>>>

---
title: "Final Exam"
editor_options: 
  chunk_output_type: console
---

@@

*Thursday, December 12, 11:30 AM -2:00 PM*

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/finalconcepts.pdf)
- [<i class="fas fa-external-link-square-alt"></i> Review Questions Slides (TBD)](/slides/final-review.html)

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/02-old-exam.pdf)

@@

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/oldexams/finalformulas.pdf)

### 2019-12-06 content/assignment/05-problem-set.Rmd
Add R Practice 21 answers
Add HW 5 answers, HW 6 and answers, finalize schedule page (put extra content after final), add final exam prep

@@

### Part A
Using the group means, write a regression equation for a regression of GDP Growth rate on Common Law, including the standard errors in parentheses below the coefficients. Define

>>>>

**ANSWERS:**

- [<i class="fas fa-file-pdf"></i> `html`](/homeworks/05-problem-set-answers.html)
- [<i class="fab fa-markdown"></i> `Markdown`](/homeworks/05-problem-set-answers.Rmd)
- [<i class="fas fa-registered"></i> `R Script`](/homeworks/05-problem-set-answers.R)

@@

### Part A
Using the group means, write a regression equation for a regression of GDP Growth rate on Common Law. Define

### 2019-12-06 content/class/21-class.Rmd
Add HW 5 answers, HW 6 and answers, finalize schedule page (put extra content after final), add final exam prep

| Linear-Log | Log-Linear | Log-Log |
|:----------:|:----------:|:-------:|
| ![](21-slides_files/figure-html/unnamed-chunk-14-1.png) | ![](21-slides_files/figure-html/unnamed-chunk-20-1.png) | ![](21-slides_files/figure-html/unnamed-chunk-25-1.png) |
| $\hat{Y_i}=\hat{\beta_0}+\hat{\beta_1}\mathbf{ln(X_i)}$ | $\mathbf{ln(\hat{Y_i})}=\hat{\beta_0}+\hat{\beta_1}X_i$ | $\mathbf{ln(\hat{Y_i})}=\hat{\beta_0}+\hat{\beta_1}\mathbf{ln(X_i)}$ |
| $R^2=0.65$ | $R^2=0.30$ | $R^2=0.61$ |

>>>>

| Linear-Log | Log-Linear | Log-Log |
|:----------:|:----------:|:-------:|
| ![](https://metricsf19.classes.ryansafner.com/slides/21-slides_files/figure-html/unnamed-chunk-14-1.png) | ![](https://metricsf19.classes.ryansafner.com/slides/21-slides_files/figure-html/unnamed-chunk-20-1.png) | ![](https://metricsf19.classes.ryansafner.com/slides/21-slides_files/figure-html/unnamed-chunk-25-1.png) |
| $\hat{Y_i}=\hat{\beta_0}+\hat{\beta_1}\mathbf{ln(X_i)}$ | $\mathbf{ln(\hat{Y_i})}=\hat{\beta_0}+\hat{\beta_1}X_i$ | $\mathbf{ln(\hat{Y_i})}=\hat{\beta_0}+\hat{\beta_1}\mathbf{ln(X_i)}$ |
| $R^2=0.65$ | $R^2=0.30$ | $R^2=0.61$ |
